%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {OutlierAI} % Organisation
    {Remote} % Location
    {october 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in training Large Language Models to evaluate their responses and behavior, ensuring robust functionality and integration.}
        \item {Developed comprehensive LLM evaluation reports, identifying model weaknesses and suggesting improvements}
        \item {writing challenging prompts to find the wake points of the LLM's responses about coding and software engineering subjects.}
        \item {\textbf{Technical Skills:}C\#, Python, Java, Latex, technical Writing.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Backend Intern} % Job title
    {DEPI} % Organisation
    {Egypt} % Location
    {MAY - OCT 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Assisted in the development and maintenance of RESTful APIs using ASP.NET Core, ensuring robust functionality and integration with front-end systems}
        \item {Utilized Entity Framework Core to design and manage database schemas, write queries, and handle migrations to support dynamic data interactions}
        \item {Understanding of software development lifecycle and agile methodologies}
        \item {\textbf{Technical Skills:}C\#, .NET Framework, Entity Framework, ASP.NET, MVC, REST API, SwaggerUI , GitHub.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management,Adaptability,  Communication, Presentation skills.}
      \end{cvitems}
    }
    
     \cventry
    {Backend Developer} % Job title
    {Freelancer} % Organisation
    {Egypt} % Location
    {2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed tailored applications for clients, ensuring high performance and scalability.}
        \item {Developed Custom Solutions: Designed and developed .NET back-end solutions for various clients, including creating APIs, integrating with third-party services, and ensuring scalability and performance.}
        \item { Engaged directly with clients to understand their needs, provide technical advice, and deliver tailored solutions. Maintained regular updates and feedback loops to ensure client satisfaction}
        \item {\textbf{Technical Skills:}C\#, .NET Framework, Entity Framework, ASP.NET, MVC, REST API, SwaggerUI , GitHub.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management,Adaptability,  Communication, Presentation skills.}
      \end{cvitems}
    }

\end{cventries}
